---
title: "effects_lba"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file plots the posterior distributions for the LBA model results, including average estimates per training condition, as well as comparisons between training conditions.

# load packages #

Make sure the working directory is the top folder with the dmc and models folder

```{r}
source ("dmc/dmc.R")
load_model ("LBA","lba_B.R") # LBA model with B=b-A parameterization 

pkg <- c("tidyverse", "RColorBrewer", "patchwork", "tidybayes")

lapply(pkg, library, character.only = TRUE)
```

# load the model #

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
load("models/ea/modelKN.RData")
```

# set the grid for the multi-panel graph #

```{r}
design <- "
  11234
  11567
"
```

# plot settings #

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 1. DRIFT RATE COMPARISONS - FIGURE 2 #

## calculate subject average medians for drift rates for TRUE - FALSE drift rate ##

```{r}
fun <- function(x){
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])            
  diff <- (untrained-name)
  c(name,untrained,diff)
}

knots.dv.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                        fun=fun,xlab="Average Rate")
knots.dv.1 <- as.data.frame(knots.dv.1)
knots.dv.1_long <- gather(knots.dv.1, training, value, name:contrast,
                          factor_key=TRUE)

#Remove contrast condition
knots.dv.1_long <- knots.dv.1_long %>% 
  filter(!training =="contrast")

#Do the same thing for tie and both
fun <- function(x){
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  diff <- (both-tie)
  c(tie,both,diff)
}

knots.dv.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("tie","both"),
                        fun=fun,xlab="Average Rate")
knots.dv.2 <- as.data.frame(knots.dv.2)
knots.dv.2_long <- gather(knots.dv.2, training, value, tie:contrast, factor_key=TRUE)

#Remove contrast condition
knots.dv.2_long <- knots.dv.2_long %>% 
  filter(!training =="contrast")

#combine data frames
dv.comb  <- rbind(knots.dv.1_long, knots.dv.2_long)
dv.comb <- droplevels(dv.comb)

#reorder the levels
dv.comb$training <- factor(dv.comb$training, 
                           levels = c("untrained", "name", "tie", "both"))
```

## FIGURE 2A ##

Plot the drift rate difference by training condition 

```{r}
p1.1 <- ggplot(dv.comb, aes(x = value, fill=training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = 'A',
       x = "Drift Rate Difference", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  # scale_y_discrete(limits=rev) +
  theme(legend.position="none")
p1.1
```

## FIGURE 2B ##

PAIRWISE COMPARISONS OF DRIFT RATE DIFFERENCE

Compute the differences

```{r}
#Name vs. untrained
fun <- function(x){
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])       
  diff <- (name-untrained)
  c(name,untrained,diff)
}

dr.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                  fun=fun,xlab="Average Rate")
dr.1 <- as.data.frame(dr.1)
dr.1_long <- gather(dr.1, training, value, name:contrast, factor_key=TRUE)

#Remove contrast condition
dr.1_long <- dr.1_long %>% 
  filter(training =="contrast")

#tie vs. untrained
fun <- function(x){
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])     
  diff <- (tie-untrained)
  c(tie,untrained,diff)
}

dr.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("tie","untrained"),
                  fun=fun,xlab="Average Rate")
dr.2 <- as.data.frame(dr.2)
dr.2_long <- gather(dr.2, training, value, tie:contrast, factor_key=TRUE)
dr.2_long <- dr.2_long %>% 
  filter(training =="contrast")

#both vs. untrained
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  untrained <- diff(x[c("mean_v.untrained.false","mean_v.untrained.true")])       
  diff <- (both-untrained)
  c(both,untrained,diff)
}

dr.3 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","untrained"),
                  fun=fun,xlab="Average Rate")
dr.3 <- as.data.frame(dr.3)
dr.3_long <- gather(dr.3, training, value, both:contrast, factor_key=TRUE)
dr.3_long <- dr.3_long %>% 
  filter(training =="contrast")

#both vs. name
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  diff <- (both-name)
  c(both,name,diff)
}

dr.4 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","name"),
                  fun=fun,xlab="Average Rate")
dr.4 <- as.data.frame(dr.4)
dr.4_long <- gather(dr.4, training, value, both:contrast, factor_key=TRUE)
dr.4_long <- dr.4_long %>% 
  filter(training =="contrast")

#both vs. tie
fun <- function(x){
  both <- diff(x[c("mean_v.both.false","mean_v.both.true")])            
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  diff <- (both-tie)
  c(both,tie,diff)
}

dr.5 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","tie"),
                  fun=fun,xlab="Average Rate")
dr.5 <- as.data.frame(dr.5)
dr.5_long <- gather(dr.5, training, value, both:contrast, factor_key=TRUE)
dr.5_long <- dr.5_long %>% 
  filter(training =="contrast")

#name vs. tie
fun <- function(x){
  name <- diff(x[c("mean_v.name.false","mean_v.name.true")])            
  tie <- diff(x[c("mean_v.tie.false","mean_v.tie.true")])            
  diff <- (name-tie)
  c(name,tie,diff)
}

dr.6 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","tie"),
                  fun=fun,xlab="Average Rate")
dr.6 <- as.data.frame(dr.6)
dr.6_long <- gather(dr.6, training, value, name:contrast, factor_key=TRUE)
dr.6_long <- dr.6_long %>% 
  filter(training =="contrast")
```

Plot the pairwise comparisons

```{r}
p1.1.1 <- ggplot(dr.1_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = 'B',
       x = "Name vs Untrained", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.1
```

```{r}
p1.1.2 <- ggplot(dr.2_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .8, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = ' ',
       x = "Tie vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.2
```

```{r}
p1.1.3 <- ggplot(dr.3_long, aes(x = value, fill=training)) +
     stat_halfeye(alpha = .7, .width = .95) +
    geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Both vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.3
```

```{r}
p1.1.4 <- ggplot(dr.4_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Both vs Name", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.4 
```

```{r}
p1.1.5 <- ggplot(dr.5_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .8, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Both vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.5
```

```{r}
p1.1.6 <- ggplot(dr.6_long, aes(x = value, fill=training)) +
     stat_halfeye(alpha = .8, .width = .95) +
    geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = NULL,
       x = "Name vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1,2), breaks = seq(-1,2,1))
p1.1.6
```

Plot in multipanel

```{r}
p_drift <- p1.1 + p1.1.1 + p1.1.2 + p1.1.3 + p1.1.4 + p1.1.5 + p1.1.6 + 
  plot_layout(design=design)
p_drift

ggsave("figures/ea/drift_rate.jpeg",
       width = 14, height = 6, dpi = 800)
```

# 2. THRESHOLDS - FIGURE 3 #

## calculate subject average medians ##

```{r}
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.name, B.untrained, B.name - B.untrained)
}

knots.b.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                 fun=fun,xlab="Threshold Name v Untrained")
knots.b.1 <- as.data.frame(knots.b.1)
knots.b.1_long <- gather(knots.b.1, training, value, name:contrast, factor_key=TRUE)

#Remove contrast condition
knots.b.1_long <- knots.b.1_long %>% 
  filter(!training =="contrast")


#Do the same for tie and both
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff/2)
  B.tie <- (tie.same+tie.diff)/2
  c(B.both, B.tie, B.both - B.tie)
}
knots.b.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","tie"),
                 fun=fun,xlab="Threshold Both v Tie")
knots.b.2 <- as.data.frame(knots.b.2)
knots.b.2_long <- gather(knots.b.2, training, value, both:contrast, factor_key=TRUE)

#Remove contrast condition
knots.b.2_long <- knots.b.2_long %>% 
  filter(!training =="contrast")

#combine data frames
b.comb  <- rbind(knots.b.1_long, knots.b.2_long)
b.comb <- droplevels(b.comb)

#reorder the levels
b.comb$training <- factor(b.comb$training, 
                          levels = c("untrained", "name", "tie", "both"))
```

## FIGURE 3A ##

plot thresholds

```{r}
p2.1 <- ggplot(b.comb, aes(x = value, fill=training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = 'A',
       x = "Threshold", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position="none")
p2.1
```

## FIGURE 3B ##

PAIRWISE COMPARISONS - FIGURE 3B

Compute the differences

```{r}
fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.name, B.untrained, B.name - B.untrained)
}

b.1 <- compare.p(hKN,show.plot=TRUE,pretty=c("name","untrained"),
                 fun=fun,xlab="Threshold Name v Untrained")
b.1 <- as.data.frame(b.1)
b.1_long <- gather(b.1, training, value, name:contrast, factor_key=TRUE)
b.1_long <- b.1_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.tie <- (tie.same+tie.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.tie, B.untrained, B.tie - B.untrained)
}

b.2 <- compare.p(hKN,show.plot=TRUE,pretty=c("tie","untrained"),
                 fun=fun,xlab="Threshold Tie v Untrained")
b.2 <- as.data.frame(b.2)
b.2_long <- gather(b.2, training, value, tie:contrast, factor_key=TRUE)
b.2_long <- b.2_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff)/2
  B.untrained <- (untrained.same+untrained.diff)/2
  c(B.both, B.untrained, B.both - B.untrained)
}

b.3 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","untrained"),
                 fun=fun,xlab="Threshold both v Untrained")
b.3 <- as.data.frame(b.3)
b.3_long <- gather(b.3, training, value, both:contrast, factor_key=TRUE)
b.3_long <- b.3_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff)/2
  B.name <- (name.same+name.diff)/2
  c(B.both, B.name, B.both - B.name)
}

b.4 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","name"),
                 fun=fun,xlab="Threshold both v name")
b.4 <- as.data.frame(b.4)
b.4_long <- gather(b.4, training, value, both:contrast, factor_key=TRUE)
b.4_long <- b.4_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.both <- (both.same+both.diff)/2
  B.tie <- (tie.same+tie.diff)/2
  c(B.both, B.tie, B.both - B.tie)
}

b.5 <- compare.p(hKN,show.plot=TRUE,pretty=c("both","tie"),
                 fun=fun,xlab="Threshold both v tie")
b.5 <- as.data.frame(b.5)
b.5_long <- gather(b.5, training, value, both:contrast, factor_key=TRUE)
b.5_long <- b.5_long %>% 
  filter(training =="contrast")

fun <- function(x){
  name.same <- (x[c( "B.name.same")])  
  tie.same <- (x[c("B.tie.same")])             
  both.same <- (x[c("B.both.same")])             
  untrained.same <- (x[c("B.untrained.same")])             
  name.diff <- (x[c("B.name.diff")])    
  tie.diff <- (x[c("B.tie.diff")]) 
  both.diff <- (x[c("B.both.diff")])  
  untrained.diff <- (x[c("B.untrained.diff")])             
  B.name <- (name.same+name.diff)/2
  B.tie <- (tie.same+tie.diff)/2
  c(B.name, B.tie, B.name - B.tie)
}

b.6<- compare.p(hKN,show.plot=TRUE,pretty=c("name","tie"),
                fun=fun,xlab="Threshold both v name")
b.6<- as.data.frame(b.6)
b.6_long <- gather(b.6, training, value, name:contrast, factor_key=TRUE)
b.6_long <- b.6_long %>% 
  filter(training =="contrast")
```

plot pairwise comparisons

```{r}
p2.1.1 <- ggplot(b.1_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = "B",
       x = "Name vs Untrained", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.1
```

```{r}
p2.1.2 <- ggplot(b.2_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Tie vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.2
```

```{r}
p2.1.3 <- ggplot(b.3_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.3
```

```{r}
p2.1.4 <- ggplot(b.4_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Name", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.4
```

```{r}
p2.1.5 <- ggplot(b.5_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.5
```

```{r}
p2.1.6 <- ggplot(b.6_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Name vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.5,0.5), breaks = seq(-1,0))
p2.1.6
```

Plot together

```{r}
p_thresh <- p2.1 + p2.1.1 + p2.1.2 + p2.1.3 + p2.1.4 + p2.1.5 + p2.1.6 +
  plot_layout(design=design)
p_thresh

ggsave("figures/ea/thresholds.jpeg",
       width = 14, height = 6, dpi = 800)
```

# 3. NON-DECISION TIME - FIGURE 4 #

## calculate subject average medians ##

```{r}
knots.t.1 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.name","t0.untrained"),
                 pretty=c("name","untrained"),xlab="Average t0")
knots.t.1 <- as.data.frame(knots.t.1)
knots.t.1_long <- gather(knots.t.1, training, value, name:contrast, factor_key=TRUE)

#Remove contrast condition
knots.t.1_long <- knots.t.1_long %>% 
  filter(!training =="contrast")

#Do the same for both and tie
knots.t.2 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.tie"),
                 pretty=c("both","tie"),xlab="Average t0")
knots.t.2 <- as.data.frame(knots.t.2)
knots.t.2_long <- gather(knots.t.2, training, value, both:contrast, factor_key=TRUE)

#Remove contrast condition
knots.t.2_long <- knots.t.2_long %>% 
  filter(!training =="contrast")

#combine data frames
t.comb  <- rbind(knots.t.1_long, knots.t.2_long)
t.comb <- droplevels(t.comb)

#reorder the levels
t.comb$training <- factor(t.comb$training, 
                          levels = c("untrained", "name", "tie", "both"))
```

## FIGURE 4A ##

NON-DECISION TIME BY TRAINING CONDITION 

```{r}
p3.1 <- ggplot(t.comb, aes(x = value, fill= training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey",alpha = 5/10) +
  labs(title = 'A',
       x = "Non-decision Time", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position="none")
p3.1
```

## FIGURE 4B ##

PAIRWISE COMPARISONS

Compute the differences between each training condition

```{r}
t.1 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.name","t0.untrained"),
                 pretty=c("name","untrained"),xlab="Average t0")
t.1 <- as.data.frame(t.1)
t.1_long <- gather(t.1, training, value, name:contrast, factor_key=TRUE)
t.1_long <- t.1_long %>% 
  filter(training =="contrast")

t.2 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.tie","t0.untrained"),
                 pretty=c("tie","untrained"),xlab="Average t0")
t.2 <- as.data.frame(t.2)
t.2_long <- gather(t.2, training, value, tie:contrast, factor_key=TRUE)
t.2_long <- t.2_long %>% 
  filter(training =="contrast")

t.3 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.untrained"),
                 pretty=c("both","untrained"),xlab="Average t0")
t.3 <- as.data.frame(t.3)
t.3_long <- gather(t.3, training, value, both:contrast, factor_key=TRUE)
t.3_long <- t.3_long %>% 
  filter(training =="contrast")

t.4 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.name"),
                 pretty=c("both","name"),xlab="Average t0")
t.4 <- as.data.frame(t.4)
t.4_long <- gather(t.4, training, value, both:contrast, factor_key=TRUE)
t.4_long <- t.4_long %>% 
  filter(training =="contrast")

t.5 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.both","t0.tie"),
                 pretty=c("both","tie"),xlab="Average t0")
t.5 <- as.data.frame(t.5)
t.5_long <- gather(t.5, training, value, both:contrast, factor_key=TRUE)
t.5_long <- t.5_long %>% 
  filter(training =="contrast")

t.6 <- compare.p(hKN,show.plot=TRUE,pnames=c("t0.name","t0.tie"),
                 pretty=c("name","tie"),xlab="Average t0")
t.6 <- as.data.frame(t.6)
t.6_long <- gather(t.6, training, value, name:contrast, factor_key=TRUE)
t.6_long <- t.6_long %>% 
  filter(training =="contrast")
```

plot pairwise comparisons

```{r}
p3.1.1 <- ggplot(t.1_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(title = 'B',
       x = "Name vs Untrained", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.1
```

```{r}
p3.1.2 <- ggplot(t.2_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Tie vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.2
```

```{r}
p3.1.3 <- ggplot(t.3_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Untrained", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.3
```

```{r}
p3.1.4 <- ggplot(t.4_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Name", y = "Density") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.4
```

```{r}
p3.1.5 <- ggplot(t.5_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Both vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.5
```

```{r}
p3.1.6 <- ggplot(t.6_long, aes(x = value, fill=training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "red",alpha = 5/10) +
  labs(x = "Name vs Tie", y = " ") +
  scale_fill_manual(values = c("darkgrey")) +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.1,0.4), breaks = seq(0,0.4,0.2))
p3.1.6
```

Arrange together
```{r}
p_ndt <- p3.1 + p3.1.1 + p3.1.2 + p3.1.3 + p3.1.4 + p3.1.5 + p3.1.6 + 
  plot_layout(design =design)
p_ndt

ggsave("figures/ea/ndt.jpeg",
       width = 14, height = 6, dpi = 800)
```
