---
title: "model_lba"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script sets up the LBA model, loads in the raw data, fits the model to the data and then samples the hLBA. 

Note - you need to make sure the working directory is the top directory with the models and dmc folder.

# load data, models and packages #

```{r}
source ("dmc/dmc.R")
load_model ("LBA","lba_B.R") # LBA model with B=b-A parameterization 

library(tidyverse)

## custom wrangle and plotting functions
source("custom_functions/wrangle_plot.R")
```


# Day 1 data #

## read in the model object (if available) ##

Load in the model object if previously run

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
# load("models/ea/day1/day1_modelKN.RData")
```

## read in the data ##

Load in the raw data (and convert names to match the labels that Sam used when fitting the LBA model)

Knots Data 
s: Subject ID (1-18)
S: Stimulus (match vs. mismatch)
GRP: Training Group (name vs. tie vs. both vs. untrained)
R: Response (same vs. different)
RT: Reaction Time (seconds)

For DMC, we also need to rename the levels of the response so that they are unique to stimulus. 

```{r}
data_lba <- read_csv("data/processed/day1_data_lba.csv") %>%
  ## rename group
  rename(GRP = GROUP) %>% 
  ## reorder
  select(s, S, GRP, R, RT) %>% 
  ## rename levels of variables
  mutate(S = if_else(S==1, "match", "mis"),
         R = if_else(R==1, "same", "diff")) %>% 
  ## create factors
  mutate(s = factor(s),
         S = factor(S,
                    levels = c("match", "mis")),
         GRP = factor(GRP,
                      levels = c("name", "tie", "both", "untrained")), ## this is the order Sam used.
         R = factor(R,
                    levels = c("same", "diff"))) %>% 
  as.data.frame() ## dmc prefers a data frame rather than a tibble
head(data_lba)
str(data_lba)
```

rename the data to match Sam's naming

```{r}
day1_data_knots <- data_lba
```

## STEP 1: Set up the Model Object ##

1) List the factors

In this design have a stimulus factor and a group factor (GRP)

```{r}
factors <- list(S=c("match","mis"), GRP=c("name","tie", "both", "untrained")) 
```

2) List of responses

```{r}
responses <- c("same","diff") # Can identify two pictures as the same or different
```

3) Match map
Specify which accumulator matches which response

```{r}
match.map <- list(M=list(match="same",mis="diff"))
```

4) p.map specifies how the model parameters match to the factors

In this design the threshold parameter (B) can be influenced by GRP and Response (R)
The drift rate parameter (mean_v) is influenced by GRP and Match
The non-decision time parameter (t0) can be influenced by the GRP factor
When specified as 1 this assumes that the parameter is the same for all accumulators

```{r}
p.map <- list(A="1",B=c("GRP", "R"),t0=c("GRP"),mean_v=c("GRP", "M"),sd_v="M",st0="1") #M needs to be put last
```

5) Constants

```{r}
const <- c(sd_v.false=1,st0=0)
```

6) Create data.model object

```{r}
model <- model.dmc(p.map,match.map=match.map,constants=const,responses=responses,
                   factors=factors)
```

Parameter vector names are: ( see attr(,"p.vector") )
 [1] "A"                      "B.name.same"            "B.tie.same"             "B.both.same"            "B.untrained.same"      
 [6] "B.name.diff"            "B.tie.diff"             "B.both.diff"            "B.untrained.diff"       "t0.name"               
[11] "t0.tie"                 "t0.both"                "t0.untrained"           "mean_v.name.true"       "mean_v.tie.true"       
[16] "mean_v.both.true"       "mean_v.untrained.true"  "mean_v.name.false"      "mean_v.tie.false"       "mean_v.both.false"     
[21] "mean_v.untrained.false" "sd_v.true"                 

Constants are (see attr(,"constants") ):
sd_v.false        st0 
         1          0 

Model type = norm (posdrift= TRUE ) 

## STEP 2: COMBINE MODEL WITH DATA ##

7) Simulate the data to make sure the model is set up correctly

```{r}
p.vector<- c(A = 1, 
             B.name.same = 0.5, 
             B.tie.same = 0.5, 
             B.both.same = 0.5, 
             B.untrained.same = 0.5, 
             B.name.diff = 0.5, 
             B.tie.diff = 0.5, 
             B.both.diff = 0.5, 
             B.untrained.diff = 0.5, 
             t0.name = .2, 
             t0.tie = .2, 
             t0.both = .2,
             t0.untrained = .2,
             mean_v.name.true = 1, 
             mean_v.tie.true = 1, 
             mean_v.both.true = 1, 
             mean_v.untrained.true = 1,
             mean_v.name.false = 0, 
             mean_v.tie.false = 0, 
             mean_v.both.false = 0, 
             mean_v.untrained.false = 0,
             sd_v.true = 0.5) #
check.p.vector(p.vector,model) #If everything ok nothing returned
print.cell.p(p.vector,model)

# Simulate this is for one subject
data <- simulate.dmc(p.vector,model,1e4)
data.model <- data.model.dmc(data,model)
plot.cell.density(data.model[data.model$S=='match',],C="same")
plot.cell.density(data.model[data.model$S=='match',],C="diff")

#This is for 20 subjects, 40 data points per subject
data1 <- h.simulate.dmc(model,ps=p.vector,ns=20,n=40)
data1.model <- data.model.dmc(data1,model)
```

8) Create the data model object

```{r}
data.model <- data.model.dmc(day1_data_knots,model)
```

Plot the first two subjects to check

```{r}
 par(mfcol=c(2,4)) 
 for (i in 1:2) {
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="name" & data.model[[i]]$S=="match",],C="same")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="name" & data.model[[i]]$S=="match",],C="diff")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="tie" & data.model[[i]]$S=="mis",],C="mis")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="tie" & data.model[[i]]$S=="mis",],C="same")
 }  
```

Save the data model object

```{r}
dmKN <- data.model
save(data.model, file = "models/ea/day1/day1_dmKN.RData")
```

## STEP 3: CREATE PRIORS ##

Threshold parameters are 1
Start point parameters is 1
Rate parameters are 1 for matching accumulators and 0 for mismatching accumulators
sv for matching is .5
t0 is .2
t0 is truncated at 1 seconds, v is unbounded, A, B, and sd

```{r}
## Standard deviations of population priors should be broad. Means should be roughly plausible values. 
pop.mean <- c(A = 1, 
             B.name.same = 0.5, 
             B.tie.same = 0.5, 
             B.both.same = 0.5, 
             B.untrained.same = 0.5, 
             B.name.diff = 0.5, 
             B.tie.diff = 0.5, 
             B.both.diff = 0.5, 
             B.untrained.diff = 0.5, 
             t0.name = .2, 
             t0.tie = .2, 
             t0.both = .2,
             t0.untrained = .2,
             mean_v.name.true = 1, 
             mean_v.tie.true = 1, 
             mean_v.both.true = 1, 
             mean_v.untrained.true = 1,
             mean_v.name.false = 0, 
             mean_v.tie.false = 0, 
             mean_v.both.false = 0, 
             mean_v.untrained.false = 0,
             sd_v.true = 0.5) #
pop.scale <-c(A = 2, 
             B.name.same = 2, 
             B.tie.same = 2, 
             B.both.same = 2, 
             B.untrained.same = 2, 
             B.name.diff = 2, 
             B.tie.diff = 2, 
             B.both.diff = 2, 
             B.untrained.diff = 2, 
             t0.name = 2, 
             t0.tie = 2, 
             t0.both = 2,
             t0.untrained = 2,
             mean_v.name.true = 2, 
             mean_v.tie.true = 2, 
             mean_v.both.true = 2, 
             mean_v.untrained.true = 2,
             mean_v.name.false = 2, 
             mean_v.tie.false = 2, 
             mean_v.both.false = 2, 
             mean_v.untrained.false = 2,
             sd_v.true = 2) #
pop.prior <- prior.p.dmc(
  dists = rep("tnorm",22),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,0,0,0,0,0,0,0,0.1,0.1,0.1,0.1,NA,NA,NA,NA,NA,NA,NA,NA,0),
  upper=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1)
)
```

Check the distributions

```{r}
par(mfcol=c(2,5)); for (i in names(pop.prior)) plot.prior(i,pop.prior)
```

## STEP 4: SAMPLING - FIT FIXED EFFECTS AND HIERARCHICAL ##

1) Specify the priors

```{r}
p.prior <- prior.p.dmc(
  dists = rep("tnorm",22),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,0,0,0,0,0,0,0,0.1,0.1,0.1,0.1,NA,NA,NA,NA,NA,NA,NA,NA,0),
  upper=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1)
)
```

2) Set up the sampling object called sKN

```{r}
sKN  <- h.samples.dmc(nmc = 120, p.prior, data.model)
```

## Automatic Script for sampling ##

Fits fixed effects first and uses these as starting appoints for the full hierarchical model

```{r}
tmp=load("models/ea/day1/day1_dmKN.RData")
cores=length(sKN)

# Fixed effects, comment out on subsequent runs
sKN <- h.RUN.dmc(sKN,cores=cores)
save(dmKN,sKN,file="models/ea/day1/day1_donesmodelKN.RData")
# Make hierarchical, comment out on subsequent runs
p.prior <- sKN[[1]]$p.prior
p1 <- get.p.vector(sKN[[1]])[names(p.prior)]
s.prior <- prior.p.dmc(p1=p1,p2=p1,
                       dists=rep("gamma",length(p1)))
pp.prior=list(p.prior,s.prior)
hstart <- make.hstart(sKN)
theta1 <- make.theta1(sKN)
hKN <- h.samples.dmc(nmc=100,p.prior,dmKN,pp.prior,
                    hstart.prior=hstart,theta1=theta1,thin=10)
rm(dmKN,sKN); gc()

# Hierarhcial fit, comment out all but the next line on subsequent runs
pp.prior <- attr(hKN,"hyper")$pp.prior
hKN  <- h.run.unstuck.dmc(hKN, p.migrate = .05, cores = cores)
save(hKN,file="models/ea/day1/day1_modelKN.RData")
hKN <- h.run.converge.dmc(h.samples.dmc(nmc=100, samples=hKN),
                      thorough=TRUE,nmc=50,cores=cores,finalrun=TRUE,finalI=250)
save(hKN,file="models/ea/day1/day1_modelKN.RData")

# Uncomment the following and make more copies to run more fits.
# hX <- h.run.dmc(h.samples.dmc(samples=hX,nmc=250),cores=cores,report=10)
# save(hX,file="models/ea/modelX.RData")


# Make diagnostics, tweak layout as desired
pdf("figures/ea/day1/day1_modelKN_chains.pdf",height=6,width = 8)
plot.dmc(hKN,hyper=TRUE,pll.chain=TRUE) 
plot.dmc(hKN,hyper=TRUE,layout=c(3,3))
plot.dmc(hKN,hyper=TRUE,layout=c(4,4),p.prior=pp.prior)
dev.off()

ppKN <- h.post.predict.dmc(hKN)
save(hKN,ppKN,file="models/ea/day1/day1_modelKN.RData")
pdf("figures/ea/day1/day1_KN_fit.pdf",height=6, width=8)
plot.pp.dmc(ppKN,model.legend = TRUE,layout=c(2,4))
dev.off()

## plot prior vs posterior
day1_pp_plots <- plot_hyper_with_prior(hKN, pp.prior, nrow = 5, ncol = 5)

# Display and save location parameters
print(day1_pp_plots$location_plot)
ggsave("figures/ea/day1_pp_location.jpeg",
       width = 12, height = 9)
# Display and save scale parameters  
print(day1_pp_plots$scale_plot)
ggsave("figures/ea/day1_pp_scale.jpeg",
       width = 12, height = 9)

h.IC.dmc(hKN,DIC=TRUE)

gelman.diag.dmc(hKN,hyper=TRUE)
gelman.diag.dmc(hKN)

parsKN <- summary.dmc(hKN,hyper=TRUE) # Summary of the hyper posterior sample
round(parsKN$quantiles[,c(1,3,5)],3)
parsKN <- summary.dmc(hKN) # Summary of the posterior samples for each participant.
save(hKN, ppKN, parsKN,file="models/ea/day1/day1_modelKN.RData")
```

## posterior predictions ##

## create a ggplot ready (i.e., tidy) list of dfs at the group level ##

This might take 30 seconds or so...

```{r}
## posterior predictions with gglist=TRUE
day1_ppKNgg <- h.post.predict.dmc(hKN, cores=8, gglist = TRUE)
group_ppX <- attr(attr(day1_ppKNgg, "av"), "gglist")
head(group_ppX)
str(group_ppX)
```

## take out relevant dfs for plotting ##

```{r}
# pps - posterior predictive
pps <- group_ppX %>% 
  pluck("pps")
head(pps)
str(pps)

# data 
# not necessary, but keeps it "tidy" i.e., one datapoint / observation per row
d <- pps %>% 
  select(S, GRP, R, data)
head(d)
str(d)

# rt quantiles
rt_q <- group_ppX %>% 
  pluck("RTs")
head(rt_q)
str(rt_q)
```

## plot accuracy ##

- dot for data
- dot and error bar for post preds

```{r}
p1.1 <- ggplot(pps, aes(x=R, y=median, 
                           fill=R, colour=R)) +
   geom_jitter(data = d,
               aes(y=data),
               position=position_jitterdodge(),
               alpha = 1, colour = "darkgrey", size = 3) +
   geom_point(alpha = 3, position = pd2, size = 3) +
   geom_line(aes(group = 1), position = pd2, colour = "black") +
   geom_errorbar(aes(ymin = lower, ymax = upper),
                width=.2, position=pd2) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   ggtitle("accuracy") +
   labs(y="accuracy (%)") + 
   facet_grid(GRP~S)
p1.1
```

## plot the the RT quantiles ##

```{r}
p1.2 <- ggplot(rt_q, aes(x=R, y=median, colour=R)) +
   geom_point(aes(y=data),
              # position = pd2,
              alpha = 1, colour = "darkgrey", size = 3) +
   geom_point(alpha = 3, size = 3) +
   geom_line(aes(group = quantile), colour = "black") +
   geom_errorbar(aes(ymin = lower, ymax = upper),
                width=.2) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   ggtitle("RT quantiles") +
   labs(y="reaction time (s)") + 
   facet_grid(GRP~S)
p1.2
```

## plot them together using patchwork ##

```{r}
p1.3 <- p1.1 | p1.2
p1.3

## you could save a figure at this point, if you wanted
ggsave("figures/ea/day1_ppreds_fit.jpeg",
       width = 10, height = 8, dpi = 800)
```


## STEP 5: PARAMETER ESTIMATES ##

List of parameters since you will use these names in the parameter tests

Parameter vector names are: ( see attr(,"p.vector") )
 [1] "A"                      "B.name.same"            "B.tie.same"             "B.both.same"            "B.untrained.same"      
 [6] "B.name.diff"            "B.tie.diff"             "B.both.diff"            "B.untrained.diff"       "t0.name"               
[11] "t0.tie"                 "t0.both"                "t0.untrained"           "mean_v.name.true"       "mean_v.tie.true"       
[16] "mean_v.both.true"       "mean_v.untrained.true"  "mean_v.name.false"      "mean_v.tie.false"       "mean_v.both.false"     
[21] "mean_v.untrained.false" "sd_v.true"        

Constants are (see attr(,"constants") ):
sd_v.false        st0 
         1          0 
         

# Day 5 data #

## read in the model object (if available) ##

Load in the model object if previously run

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
# load("models/ea/modelKN.RData")
```

## read in the data ##

Load in the raw data (and convert names to match the labels that Sam used when fitting the LBA model)

Knots Data 
s: Subject ID (1-18)
S: Stimulus (match vs. mismatch)
GRP: Training Group (name vs. tie vs. both vs. untrained)
R: Response (same vs. different)
RT: Reaction Time (seconds)

For DMC, we also need to rename the levels of the response so that they are unique to stimulus. 

```{r}
data_lba <- read_csv("data/processed/day5_data_lba.csv") %>%
  ## rename group
  rename(GRP = GROUP) %>% 
  ## reorder
  select(s, S, GRP, R, RT) %>% 
  ## rename levels of variables
  mutate(S = if_else(S==1, "match", "mis"),
         R = if_else(R==1, "same", "diff")) %>% 
  ## create factors
  mutate(s = factor(s),
         S = factor(S,
                    levels = c("match", "mis")),
         GRP = factor(GRP,
                      levels = c("name", "tie", "both", "untrained")), ## this is the order Sam used.
         R = factor(R,
                    levels = c("same", "diff"))) %>% 
  as.data.frame() ## dmc prefers a data frame rather than a tibble
head(data_lba)
str(data_lba)
```

rename the data to match Sam's naming

```{r}
data_knots <- data_lba
```

## STEP 1: Set up the Model Object ##

1) List the factors

In this design have a stimulus factor and a group factor (GRP)

```{r}
factors <- list(S=c("match","mis"), GRP=c("name","tie", "both", "untrained")) 
```

2) List of responses

```{r}
responses <- c("same","diff") # Can identify two pictures as the same or different
```

3) Match map
Specify which accumulator matches which response

```{r}
match.map <- list(M=list(match="same",mis="diff"))
```

4) p.map specifies how the model parameters match to the factors

In this design the threshold parameter (B) can be influenced by GRP and Response (R)
The drift rate parameter (mean_v) is influenced by GRP and Match
The non-decision time parameter (t0) can be influenced by the GRP factor
When specified as 1 this assumes that the parameter is the same for all accumulators

```{r}
p.map <- list(A="1",B=c("GRP", "R"),t0=c("GRP"),mean_v=c("GRP", "M"),sd_v="M",st0="1") #M needs to be put last
```

5) Constants

```{r}
const <- c(sd_v.false=1,st0=0)
```

6) Create data.model object

```{r}
model <- model.dmc(p.map,match.map=match.map,constants=const,responses=responses,
                   factors=factors)
```

Parameter vector names are: ( see attr(,"p.vector") )
 [1] "A"                      "B.name.same"            "B.tie.same"             "B.both.same"            "B.untrained.same"      
 [6] "B.name.diff"            "B.tie.diff"             "B.both.diff"            "B.untrained.diff"       "t0.name"               
[11] "t0.tie"                 "t0.both"                "t0.untrained"           "mean_v.name.true"       "mean_v.tie.true"       
[16] "mean_v.both.true"       "mean_v.untrained.true"  "mean_v.name.false"      "mean_v.tie.false"       "mean_v.both.false"     
[21] "mean_v.untrained.false" "sd_v.true"                 

Constants are (see attr(,"constants") ):
sd_v.false        st0 
         1          0 

Model type = norm (posdrift= TRUE ) 

## STEP 2: COMBINE MODEL WITH DATA ##

7) Simulate the data to make sure the model is set up correctly

```{r}
p.vector<- c(A = 1, 
             B.name.same = 0.5, 
             B.tie.same = 0.5, 
             B.both.same = 0.5, 
             B.untrained.same = 0.5, 
             B.name.diff = 0.5, 
             B.tie.diff = 0.5, 
             B.both.diff = 0.5, 
             B.untrained.diff = 0.5, 
             t0.name = .2, 
             t0.tie = .2, 
             t0.both = .2,
             t0.untrained = .2,
             mean_v.name.true = 1, 
             mean_v.tie.true = 1, 
             mean_v.both.true = 1, 
             mean_v.untrained.true = 1,
             mean_v.name.false = 0, 
             mean_v.tie.false = 0, 
             mean_v.both.false = 0, 
             mean_v.untrained.false = 0,
             sd_v.true = 0.5) #
check.p.vector(p.vector,model) #If everything ok nothing returned
print.cell.p(p.vector,model)

# Simulate this is for one subject
data <- simulate.dmc(p.vector,model,1e4)
data.model <- data.model.dmc(data,model)
plot.cell.density(data.model[data.model$S=='match',],C="same")
plot.cell.density(data.model[data.model$S=='match',],C="diff")

#This is for 20 subjects, 40 data points per subject
data1 <- h.simulate.dmc(model,ps=p.vector,ns=20,n=40)
data1.model <- data.model.dmc(data1,model)
```

8) Create the data model object

```{r}
data.model <- data.model.dmc(data_knots,model)
```

Plot the first two subjects to check

```{r}
 par(mfcol=c(2,4)) 
 for (i in 1:2) {
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="name" & data.model[[i]]$S=="match",],C="same")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="name" & data.model[[i]]$S=="match",],C="diff")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="tie" & data.model[[i]]$S=="mis",],C="mis")
   plot.cell.density(data.cell=data.model[[i]][data.model[[i]]$GRP=="tie" & data.model[[i]]$S=="mis",],C="same")
 }  
```

Save the data model object

```{r}
dmKN <- data.model
save(data.model, file = "data/ea/models/dmKN.RData")
```

## STEP 3: CREATE PRIORS ##

Threshold parameters are 1
Start point parameters is 1
Rate parameters are 1 for matching accumulators and 0 for mismatching accumulators
sv for matching is .5
t0 is .2
t0 is truncated at 1 seconds, v is unbounded, A, B, and sd

```{r}
## Standard deviations of population priors should be broad. Means should be roughly plausible values. 
pop.mean <- c(A = 1, 
             B.name.same = 0.5, 
             B.tie.same = 0.5, 
             B.both.same = 0.5, 
             B.untrained.same = 0.5, 
             B.name.diff = 0.5, 
             B.tie.diff = 0.5, 
             B.both.diff = 0.5, 
             B.untrained.diff = 0.5, 
             t0.name = .2, 
             t0.tie = .2, 
             t0.both = .2,
             t0.untrained = .2,
             mean_v.name.true = 1, 
             mean_v.tie.true = 1, 
             mean_v.both.true = 1, 
             mean_v.untrained.true = 1,
             mean_v.name.false = 0, 
             mean_v.tie.false = 0, 
             mean_v.both.false = 0, 
             mean_v.untrained.false = 0,
             sd_v.true = 0.5) #
pop.scale <-c(A = 2, 
             B.name.same = 2, 
             B.tie.same = 2, 
             B.both.same = 2, 
             B.untrained.same = 2, 
             B.name.diff = 2, 
             B.tie.diff = 2, 
             B.both.diff = 2, 
             B.untrained.diff = 2, 
             t0.name = 2, 
             t0.tie = 2, 
             t0.both = 2,
             t0.untrained = 2,
             mean_v.name.true = 2, 
             mean_v.tie.true = 2, 
             mean_v.both.true = 2, 
             mean_v.untrained.true = 2,
             mean_v.name.false = 2, 
             mean_v.tie.false = 2, 
             mean_v.both.false = 2, 
             mean_v.untrained.false = 2,
             sd_v.true = 2) #
pop.prior <- prior.p.dmc(
  dists = rep("tnorm",22),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,0,0,0,0,0,0,0,0.1,0.1,0.1,0.1,NA,NA,NA,NA,NA,NA,NA,NA,0),
  upper=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1)
)
```

Check the distributions

```{r}
par(mfcol=c(2,5)); for (i in names(pop.prior)) plot.prior(i,pop.prior)
```

## STEP 4: SAMPLING - FIT FIXED EFFECTS AND HIERARCHICAL ##

1) Specify the priors

```{r}
p.prior <- prior.p.dmc(
  dists = rep("tnorm",22),
  p1=pop.mean,p2=pop.scale,
  lower=c(0,0,0,0,0,0,0,0,0,0.1,0.1,0.1,0.1,NA,NA,NA,NA,NA,NA,NA,NA,0),
  upper=c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,1)
)
```

2) Set up the sampling object called sKN

```{r}
sKN  <- h.samples.dmc(nmc = 120, p.prior, data.model)
```

## Automatic Script for sampling ##

Fits fixed effects first and uses these as starting appoints for the full hierarchical model

```{r}
tmp=load("models/ea/dmKN.RData")
cores=length(sKN)

# Fixed effects, comment out on subsequent runs
sKN <- h.RUN.dmc(sKN,cores=cores)
save(dmKN,sKN,file="models/ea/donesmodelKN.RData")
# Make hierarchical, comment out on subsequent runs
p.prior <- sKN[[1]]$p.prior
p1 <- get.p.vector(sKN[[1]])[names(p.prior)]
s.prior <- prior.p.dmc(p1=p1,p2=p1,
                       dists=rep("gamma",length(p1)))
pp.prior=list(p.prior,s.prior)
hstart <- make.hstart(sKN)
theta1 <- make.theta1(sKN)
hKN <- h.samples.dmc(nmc=100,p.prior,dmKN,pp.prior,
                    hstart.prior=hstart,theta1=theta1,thin=10)
rm(dmKN,sKN); gc()

# Hierarhcial fit, comment out all but the next line on subsequent runs
pp.prior <- attr(hKN,"hyper")$pp.prior
hKN  <- h.run.unstuck.dmc(hKN, p.migrate = .05, cores = cores)
save(hKN,file="models/ea/modelKN.RData")
hKN <- h.run.converge.dmc(h.samples.dmc(nmc=100, samples=hKN),
                      thorough=TRUE,nmc=50,cores=cores,finalrun=TRUE,finalI=250)
save(hKN,file="models/ea/modelKN.RData")

# Uncomment the following and make more copies to run more fits.
# hX <- h.run.dmc(h.samples.dmc(samples=hX,nmc=250),cores=cores,report=10)
# save(hX,file="models/ea/modelX.RData")


# Make diagnostics, tweak layout as desired
pdf("figures/ea/day5_modelKN_chains.pdf",height=6,width = 8)
plot.dmc(hKN,hyper=TRUE,pll.chain=TRUE) 
plot.dmc(hKN,hyper=TRUE,layout=c(3,3))
plot.dmc(hKN,hyper=TRUE,layout=c(4,4),p.prior=pp.prior)
dev.off()

ppKN <- h.post.predict.dmc(hKN)
save(hKN,ppKN,file="models/ea/modelKN.RData")
pdf("figures/ea/day5_KN_fit.pdf",height=6, width=8)
plot.pp.dmc(ppKN,model.legend = TRUE,layout=c(2,4))
dev.off()

## plot prior vs posterior
day5_pp_plots <- plot_hyper_with_prior(hKN, pp.prior, nrow = 5, ncol = 5)

# Display and save location parameters
print(day5_pp_plots$location_plot)
ggsave("figures/ea/day5_pp_location.jpeg",
       width = 12, height = 9)
# Display and save scale parameters  
print(day5_pp_plots$scale_plot)
ggsave("figures/ea/day5_pp_scale.jpeg",
       width = 12, height = 9)

h.IC.dmc(hKN,DIC=TRUE)

gelman.diag.dmc(hKN,hyper=TRUE)
gelman.diag.dmc(hKN)

parsKN <- summary.dmc(hKN,hyper=TRUE) # Summary of the hyper posterior sample
round(parsKN$quantiles[,c(1,3,5)],3)
parsKN <- summary.dmc(hKN) # Summary of the posterior samples for each participant.
save(hKN, ppKN, parsKN,file="models/ea/modelKN.RData")
```

## posterior predictions ##

## create a ggplot ready (i.e., tidy) list of dfs at the group level ##

This might take 30 seconds or so...

```{r}
## posterior predictions with gglist=TRUE
day5_ppKNgg <- h.post.predict.dmc(hKN, cores=8, gglist = TRUE)
group_ppX <- attr(attr(day5_ppKNgg, "av"), "gglist")
head(group_ppX)
str(group_ppX)
```

## take out relevant dfs for plotting ##

```{r}
# pps - posterior predictive
pps <- group_ppX %>% 
  pluck("pps")
head(pps)
str(pps)

# data 
# not necessary, but keeps it "tidy" i.e., one datapoint / observation per row
d <- pps %>% 
  select(S, GRP, R, data)
head(d)
str(d)

# rt quantiles
rt_q <- group_ppX %>% 
  pluck("RTs")
head(rt_q)
str(rt_q)
```

## plot accuracy ##

- dot for data
- dot and error bar for post preds

```{r}
p2.1 <- ggplot(pps, aes(x=R, y=median, 
                           fill=R, colour=R)) +
   geom_jitter(data = d,
               aes(y=data),
               position=position_jitterdodge(),
               alpha = 1, colour = "darkgrey", size = 3) +
   geom_point(alpha = 3, position = pd2, size = 3) +
   geom_line(aes(group = 1), position = pd2, colour = "black") +
   geom_errorbar(aes(ymin = lower, ymax = upper),
                width=.2, position=pd2) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   ggtitle("accuracy") +
   labs(y="accuracy (%)") + 
   facet_grid(GRP~S)
p2.1
```

## plot the the RT quantiles ##

```{r}
p2.2 <- ggplot(rt_q, aes(x=R, y=median, colour=R)) +
   geom_point(aes(y=data),
              # position = pd2,
              alpha = 1, colour = "darkgrey", size = 3) +
   geom_point(alpha = 3, size = 3) +
   geom_line(aes(group = quantile), colour = "black") +
   geom_errorbar(aes(ymin = lower, ymax = upper),
                width=.2) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
   ggtitle("RT quantiles") +
   labs(y="reaction time (s)") + 
   facet_grid(GRP~S)
p2.2
```

## plot them together using patchwork ##

```{r}
p2.3 <- p2.1 | p2.2
p2.3

## you could save a figure at this point, if you wanted
ggsave("figures/ea/day5_ppreds_fit.jpeg",
       width = 10, height = 8, dpi = 800)
```

## STEP 5: PARAMETER ESTIMATES ##

List of parameters since you will use these names in the parameter tests

Parameter vector names are: ( see attr(,"p.vector") )
 [1] "A"                      "B.name.same"            "B.tie.same"             "B.both.same"            "B.untrained.same"      
 [6] "B.name.diff"            "B.tie.diff"             "B.both.diff"            "B.untrained.diff"       "t0.name"               
[11] "t0.tie"                 "t0.both"                "t0.untrained"           "mean_v.name.true"       "mean_v.tie.true"       
[16] "mean_v.both.true"       "mean_v.untrained.true"  "mean_v.name.false"      "mean_v.tie.false"       "mean_v.both.false"     
[21] "mean_v.untrained.false" "sd_v.true"        

Constants are (see attr(,"constants") ):
sd_v.false        st0 
         1          0 

