---
title: "wrangle"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the main data wrangling file for the analysis of knots data from Cross et al. (2012).

This script loads the processed data, wrangles the data, makes summary plots and writes out dataframes that are appropriate for the different types of analyses that will follow in the modelling scripts.

```{r setup}
pkg <- c(
  "tidyverse",
  "RColorBrewer",
  "patchwork",
  "styler",
  "gghalves",
  "ggdist",
  "janitor"
)

lapply(pkg, library, character.only = TRUE)

## theme settings for ggplot
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)

## custom wrangle and plotting functions
source("custom_functions/wrangle_plot.R")
```

# 1. load the data #

this is the processed data for day 1 session 1 and day 5 session 2

```{r}
## day 1 data
day1_raw <- read_csv("data/processed/day1_pre_knots_data.csv")
head(day1_raw)

## day 5 data
day5_raw <- read_csv("data/processed/day5_post_knots_data.csv")
head(day5_raw)
```

And this is the simulated data for code checking purposes, as the raw data cannot be made publicly available. 
If you have not requested the raw data privately, then uncomment the code chunk below and run the code.
See the sim_data.Rmd script for details on how the data were simulated. 
Note - the simulated data resemble the real data, but they will of course produce DIFFERENT results.
 
```{r}
## day 1 simulated data
# day1_raw <- read_csv("data/simulated/day1_sim_raw.csv")
# head(day1_raw)

## day 5 simulated data
# day5_raw <- read_csv("data/simulated/day5_sim_raw.csv")
# head(day5_raw)
```

combine the day 1 and day 5 data

```{r}
raw <- bind_rows(day1_raw, day5_raw)
head(raw)
glimpse(raw)
```

do some checks 

```{r}
## only day 1, session and day 5, session 2
raw %>%
  distinct(DAY, SESSION)

## 18 PIDs, PID 3 and 17 did not complete day 5, session 2 
raw %>% 
  distinct(PID)
```

# 2. do some wrangling #

select relevant variables.
create an accuracy variable.
rename group.
create factors.

```{r}
data <- raw %>%
  select(PID, DAY, SESSION, GROUP, MATCH, RESPONSE, RT)  |>  
  mutate(ACC = if_else(MATCH == RESPONSE, 1, 0))  |> 
  mutate(
    DAY = case_when(
      DAY == 1 ~ "Day 1",
      .default = "Day 5"
    ),
    GROUP = case_when(
      GROUP == 1 ~ "name",
      GROUP == 2 ~ "tie",
      GROUP == 3 ~ "both",
      .default = "untrained"
    )
  )  |> 
  mutate(
    PID = factor(PID),
    DAY = factor(DAY),
    GROUP = factor(GROUP, levels = c("untrained", "name", "tie", "both"))
  )
head(data)
glimpse(data)
```

```{r}
# Relevant variables as follows:
# PID = ID each participants should be n = 18 (with day 5, session 2 data)
# DAY = day 1 or day 5
# SESSION = session 1 or session 2
# RESPONSE = Whether the participant selects a match or not? (1 = match, 2 = mismatch)
# RT = Response times in ms
# GROUP = 1-4 (name, tie, both, untrained)
# MATCH = Whether they match or not (1 = match and 2 = mismatch)
# ACC = correct = 1, incorrect = 0
```

create a reaction time dataframe

```{r}
data_rt <- data %>% 
  filter(ACC==1)
data_rt
```

# 3. take a quick look at the data #

trial count per PID

```{r}
trials_pid <- data %>%
  group_by(PID, DAY) %>%
  tally() %>% 
  arrange(n) # take a look at the lowest trial count
head(trials_pid)
```

per condition

```{r}
trials_cond <- data %>%
  group_by(DAY, GROUP) %>%
  tally() %>% 
  arrange(n) # take a look at the lowest trial count
head(trials_cond)
```

per PID and condition

```{r}
trials_pid_cond <- data %>%
  group_by(PID, DAY, GROUP) %>%
  tally() %>% 
  arrange(n) 
head(trials_pid_cond)
```

and print it

```{r}
trials_pid_cond %>% 
  print(n=Inf)
```

# 4. create summary data #

## accuracy ##

```{r}
acc_ind <- summarise_individual(
  data,
  id_var = PID,
  group_vars = c("DAY", "GROUP"),
  response_var = ACC,
  scale = 100
)
acc_ind

acc_group <- summarise_group(
  data,
  id_var = PID,
  group_vars = c("DAY", "GROUP"),
  response_var = ACC,
  scale = 100
)
acc_group
```

## rt ##

```{r}
rt_ind <- summarise_individual(
  data_rt,
  id_var = PID,
  group_vars = c("DAY", "GROUP"),
  response_var = RT
)
rt_ind

rt_group <- summarise_group(
  data_rt,
  id_var = PID,
  group_vars = c("DAY", "GROUP"),
  response_var = RT
)
rt_group
```

## wrangle grop-level summary data for supplementary materials ##

```{r}
acc_rt_group <- bind_rows(acc_group, rt_group) |> 
  mutate(variable = rep(c("Accuracy (% correct)", "Reaction time (ms)" ), each = 8)) |> 
  clean_names() |> 
  rename(condition = group, mean = mean_val, sem = sem_val) |> 
  select(variable, day, condition, mean, sem)
acc_rt_group  
```

# 5. make some plots #

## custom raincloud plots ##

plot accuracy

```{r}
p5.1 <- plot_rain(
  acc_ind,
  acc_group,
  x_var = "GROUP",
  y_var = "mean_val",
  facet_var = "DAY",
  x_label = "Training Condition",
  y_label = "Percentage Correct",
  point_spread = .1
)
p5.1
```

plot rt

```{r}
p5.2 <- plot_rain(
  rt_ind,
  rt_group,
  x_var = "GROUP",
  y_var = "mean_val",
  facet_var = "DAY",
  x_label = "Training Condition",
  y_label = "Mean Reaction Time (ms)",
  point_spread = .1
)
p5.2
```

plot together

```{r}
p5.3 <- (p5.1 / p5.2) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(axes = "collect")
p5.3

ggsave("figures/descriptive/rain_acc_rt.jpeg",
       width = 10, height = 10, dpi = 800)
```

# 6. write out the data #

## day 1 vs 5 data for plotting and modelling via brms ##

This is the data for acc and rt labelled as it is in plots.
It can be used for modelling in the manifest analysis of rt and acc separately.

```{r}
write_csv(data, "data/processed/data_acc.csv")
write_csv(data_rt, "data/processed/data_rt.csv")
```

## day 1 vs 5 group-level summary data for supplementary materials ##

```{r}
write_csv(acc_rt_group, "tables/manifest/descriptives.csv")
```

## data for use in LBA modelling ##

this is for modelling with DMC software when using an LBA model.
DMC has specific rules about how the data are structured.

Rules for data to be used in dmc

1) Make sure you have an "s" column identifying the data for each subject that is a factor
2) Follow that by columns specifying the factors in your design. Again each must be a factor
3) The second last column give the response (again a factor)
4) The last columns is called RT, make sure the unit is seconds.

And we can remove the ACC column as DMC makes the match between Stimulus and Response.

### day 1, session 1 ###

```{r}
day1_data_lba <- data  |> 
  filter(DAY == "Day 1") |> 
  select(-DAY) |> 
  rename(s = PID, S = MATCH, R = RESPONSE)  |>  
  mutate(RT = RT/1000,
         S = factor(S),
         R = factor(R))  |> 
  select(s, GROUP, S, R, RT) |> 
  as.data.frame()
head(day1_data_lba)
  
## technically, since we are saving out a .csv file then reading it in when we get to the model script the factors and data frame (vs tibble) are not necessary here as they will need to be re-done when they are read in later. But I think it is probably good practice to get this in the format that is later required.
```

save it as a .csv file

```{r}
write_csv(day1_data_lba, "data/processed/day1_data_lba.csv")
```

### day 5, session 2 ###

```{r}
day5_data_lba <- data  |> 
  filter(DAY == "Day 5") |> 
  select(-DAY) |> 
  rename(s = PID, S = MATCH, R = RESPONSE)  |>  
  mutate(RT = RT/1000,
         S = factor(S),
         R = factor(R))  |> 
  select(s, GROUP, S, R, RT) |> 
  as.data.frame()
head(day5_data_lba)
  
## technically, since we are saving out a .csv file then reading it in when we get to the model script the factors and data frame (vs tibble) are not necessary here as they will need to be re-done when they are read in later. But I think it is probably good practice to get this in the format that is later required.
```

save it as a .csv file

```{r}
write_csv(day5_data_lba, "data/processed/day5_data_lba.csv")
```

