---
title: "day1_effects_lba"
author: "Sam & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file plots the posterior distributions for the LBA model results for the day 1, session 1 data, including average estimates per training condition, as well as comparisons between training conditions.

# load packages #

Make sure the working directory is the top folder with the dmc and models folder

```{r}
source ("dmc/dmc.R")
load_model ("LBA","lba_B.R") # LBA model with B=b-A parameterization 

pkg <- c("tidyverse", "RColorBrewer", "patchwork", "tidybayes", "styler")

lapply(pkg, library, character.only = TRUE)
```

# load the model #

```{r}
## The model object is available upon request
## Please email Samantha Parker (samantha.parker@students.mq.edu.au) or Richard Ramsey (richard.ramsey@hest.ethz.ch)
load("models/ea/day1/day1_modelKN.RData")
```

# plot settings #

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 1. Wrangle the posterior distribution #

## wrangle the samples into a tidy format ##

transpose samples and pluck theta out into a list of arrays

```{r}
array_theta <- hKN |> 
  transpose() |>  
  pluck("theta")
summary(array_theta)
str(array_theta)
```

make it tidy

```{r}
## and now use the slightly longer way with map and tidyr
theta_pid <- map(array_theta, ~ as_tibble(., rownames = "chain")) |>
  list_rbind(names_to = "pid") |>
  rename_with(~ str_replace_all(.x, '\\.', '_')) |> ## replace periods with underscores in names, as things work better below without periods in names
  pivot_longer(
    -c(pid, chain),
    values_to = "value",
    names_to = c("param", "iter"), ## this is the order of the array
    names_pattern = "([A-Za-z_\\d?]+)_(\\d+)"
  ) |> ## letters, _, optional digit before the underscore separator. digits after the underscore separator
  select(pid, iter, chain, param, value) %>% ## reorder columns
  arrange(pid, iter, chain, param) |>
  mutate(param = factor(param), pid = factor(pid)) |> ## create factors
  mutate_if(is.character, as.integer) ## change from characters to integers
summary(theta_pid)
str(theta_pid)
head(theta_pid)

## data check for param
theta_pid |>
  distinct(param) |>
  print(n = Inf)

## ok, the df has 6534000 rows.
## this makes sense to me. 18 pid x 250 iter x 66 chains * 22 params = 6534000
## 18*250*66*22
## =6534000
```

## create a group summary distribution ##

summarise across pid (to be consistent with the DMC compare.p function)

```{r}
theta_group <- theta_pid |>
  group_by(iter, chain, param) |>
  summarise(value = mean(value)) |>
  ungroup() |>
  add_column(pid = "average") |> ## add a column which makes clear it is the avg. not needed but useful for plotting later
  relocate(pid, .before = everything())
head(theta_group)
glimpse(theta_group)

## 6534000/18pid = 363000 rows
```

## calculate quantiles ##

calculate quantiles per parameter at the group level

```{r}
theta_group_q <- theta_group %>%
  group_by(param) %>%
  median_qi(value)
theta_group_q
```

and do the same per pid

```{r}
theta_pid_q <- theta_pid %>%
  group_by(pid, param) %>%
  median_qi(value)
theta_pid_q
```

# 2. Threshold plots #

## wrangle threshold values ##

calculate average thresholds at the group level

```{r}
thresh_group <- theta_group |>
  filter(str_detect(param, "B_")) |>
  separate(param, into = c("param", "training", "response"), sep = "_") |>
  pivot_wider(names_from = "response", values_from = "value") |>
  group_by(training) |>
  mutate(
    value = (diff + same) / 2,
    training = factor(training, levels = c("untrained", "name", "tie", "both")),
    draw = row_number()
  ) |>
  select(chain, iter, draw, training, value) |>
  rename(.chain = chain, .iteration = iter, .draw = draw)
head(thresh_group)
str(thresh_group)
summary(thresh_group)
```

calculate contrasts between training conditions 

```{r}
thresh_contrasts <- thresh_group |>
  compare_levels(
    value,
    by = training
  ) |>
  rename(contrast = training) |>
  mutate(
    contrast = factor(
      contrast,
      levels = c(
        "name - untrained",
        "tie - untrained",
        "both - untrained",
        "both - name",
        "both - tie",
        "tie - name"
      )
    )
  )
head(thresh_contrasts)
str(thresh_contrasts)
summary(thresh_contrasts)
```

## plot condition avg threshold data ##

```{r}
p2.1 <- ggplot(thresh_group, aes(x = value, fill = training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(x = "Threshold", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p2.1
```

## plot contrasts ##

```{r}
p2.2 <- ggplot(thresh_contrasts, aes(x = value)) +
  stat_halfeye(alpha = .7, .width = .95, fill = "darkgrey") +
  geom_vline(xintercept = 0, color = "red", alpha = 5/10) +
  labs(x = "Threshold", y = "Density") +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.2,1.5), breaks = seq(-1,1)) +
  facet_wrap(~contrast, nrow = 2)
p2.2
```

## combine plots ##

```{r}
p2.3 <- (p2.1 | p2.2) +
  plot_annotation(tag_levels = "A") +
  plot_layout(widths = c(1,2))
p2.3

ggsave("figures/ea/day1/day1_thresholds.jpeg",
       width = 14, height = 6, dpi = 800)
```

# 3. Drift rate plots #

## wrangle drift rate values ##

calculate average thresholds at the group level

```{r}
drift_group <- theta_group |>
  filter(str_detect(param, "mean_v")) |>
  mutate(param = str_remove(param, "mean_")) |>
  separate(param, into = c("param", "training", "accuracy"), sep = "_") |>
  pivot_wider(names_from = "accuracy", values_from = "value") |>
  group_by(training) |>
  mutate(
    value = true - false,
    training = factor(training, levels = c("untrained", "name", "tie", "both")),
    draw = row_number()
  ) |>
  select(chain, iter, draw, training, value) |>
  rename(.chain = chain, .iteration = iter, .draw = draw)
head(drift_group)
str(drift_group)
summary(drift_group)
```

calculate contrasts between training conditions 

```{r}
drift_contrasts <- drift_group |>
  compare_levels(
    value,
    by = training
  ) |>
  rename(contrast = training) |>
  mutate(
    contrast = factor(
      contrast,
      levels = c(
        "name - untrained",
        "tie - untrained",
        "both - untrained",
        "both - name",
        "both - tie",
        "tie - name"
      )
    )
  )
head(drift_contrasts)
str(drift_contrasts)
summary(drift_contrasts)
```

## plot condition avg drift rate ##

```{r}
p3.1 <- ggplot(drift_group, aes(x = value, fill = training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(x = "Drift rate", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p3.1
```

## plot contrasts ##

```{r}
p3.2 <- ggplot(drift_contrasts, aes(x = value)) +
  stat_halfeye(alpha = .7, .width = .95, fill = "darkgrey") +
  geom_vline(xintercept = 0, color = "red", alpha = 5/10) +
  labs(x = "Drift rate", y = "Density") +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-1.2,1.5), breaks = seq(-1,1)) +
  facet_wrap(~contrast, nrow = 2)
p3.2
```

## combine plots ##

```{r}
p3.3 <- (p3.1 | p3.2) +
  plot_annotation(tag_levels = "A") +
  plot_layout(widths = c(1,2))
p3.3

ggsave("figures/ea/day1/day1_drift_rate.jpeg",
       width = 14, height = 6, dpi = 800)
```

# 4. Non-decision time plots #

## wrangle ndt values ##

calculate average thresholds at the group level

```{r}
ndt_group <- theta_group |>
  filter(str_detect(param, "t0")) |>
  separate(param, into = c("param", "training"), sep = "_") |>
  group_by(training) |> 
  mutate(
    training = factor(training, levels = c("untrained", "name", "tie", "both")),
    draw = row_number()
  ) |>
  select(chain, iter, draw, training, value) |>
  rename(.chain = chain, .iteration = iter, .draw = draw)
head(ndt_group)
str(ndt_group)
summary(ndt_group)
```

calculate contrasts between training conditions 

```{r}
ndt_contrasts <- ndt_group |>
  compare_levels(
    value,
    by = training
  ) |>
  rename(contrast = training) |>
  mutate(
    contrast = factor(
      contrast,
      levels = c(
        "name - untrained",
        "tie - untrained",
        "both - untrained",
        "both - name",
        "both - tie",
        "tie - name"
      )
    )
  )
head(ndt_contrasts)
str(ndt_contrasts)
summary(ndt_contrasts)
```

## plot condition avg ndt rate ##

```{r}
p4.1 <- ggplot(ndt_group, aes(x = value, fill = training, y = training)) +
  stat_halfeye(alpha = .7, .width = .95) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(x = "Non-decision time", y = "Training Condition") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "none")
p4.1
```

## plot contrasts ##

```{r}
p4.2 <- ggplot(ndt_contrasts, aes(x = value)) +
  stat_halfeye(alpha = .7, .width = .95, fill = "darkgrey") +
  geom_vline(xintercept = 0, color = "red", alpha = 5/10) +
  labs(x = "Non-decision time", y = "Density") +
  theme(legend.position = "none") +
  scale_x_continuous(limits=c(-0.5,0.5), breaks = seq(-0.5,0.5,0.5)) +
  facet_wrap(~contrast, nrow = 2)
p4.2
```

## combine plots ##

```{r}
p4.3 <- (p4.1 | p4.2) +
  plot_annotation(tag_levels = "A") +
  plot_layout(widths = c(1,2))
p4.3

ggsave("figures/ea/day1/day1_ndt.jpeg",
       width = 14, height = 6, dpi = 800)
```

