---
title: "packages"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file installs packages.

There is no need to do this after the first installation, as it should all be 
controlled by renv(). 

This file is just for Rich's benefit, so that he can see how he installed them.

And this is not all of the packages. It is just the ones for writing manuscripts.

# install the libraries that we will be using #

## install ##

Next, packages for papaja and manuscript writing

```{r install-pkg}
# install.packages(c("devtools", "remotes"))
# 
devtools::install_github("crsh/papaja")
devtools::install_github("crsh/citr")
# 
install.packages("tinytex")
tinytex::install_tinytex()
# 
# # and now some useful addins for writing .Rmd from R Studio word count
devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
# 
# # remedy for shortcuts in markdown writing
remotes::install_github("ThinkR-open/remedy")
# 
# # grammar checking - cool...
devtools::install_github("ropenscilabs/gramr")
```

Finally, use renv() to take a snapshot of installed packages and update the lock.file 

```{r snapshot-renv}
# take a snapshot and update the lock.file
renv::snapshot() # this is only necessary when new packages or installed or packages are updated.
```